An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-16 indicators/code/indicator-paper-figures.Rmd
Better document indicator code

---
title: COVIDcast Indicators figures and tables
author: Alex Reinhart, et al.
date: June 23, 2021
---

@@

This file can be knit to HTML using
`rmarkdown::render("indicator-paper-figures.Rmd")` from within R, using the
[rmarkdown package](https://cran.r-project.org/package=rmarkdown). By default it
also saves publication-ready PDF versions of figures to the `../paper/fig/`
directory.

@@

```{r figure-7, message=FALSE, cache=TRUE}
cdc <- read.csv("COVID-19_Vaccinations_in_the_United_States_County.csv") %>%
  filter(Date == "07/20/2021")

>>>>

---
title: COVIDcast Indicators figures and tables
author: Alex Reinhart, et al.
date: October 16, 2021
---

@@

This file can be knit to HTML using
`rmarkdown::render("indicator-paper-figures.Rmd")` from within R, using the
[rmarkdown package](https://cran.r-project.org/package=rmarkdown). By default it
saves publication-ready PDF versions of figures to the `../paper/fig/`
directory.

This file was run with R version 4.0.4 and the versions of all packages
available in October 2021.

@@

```{r figure-7, message=FALSE, cache=TRUE}
cdc <- read.csv("COVID-19_Vaccinations_in_the_United_States_County.csv.gz") %>%
  filter(Date == "07/20/2021")

### 2021-10-16 indicators/paper/paper.tex

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID-19 Trends and Impact Survey receives an average of 50,000 responses
daily, and has received over 25 million responses since April 2020
\cite{Salomon:2021, Kreuter:2020}. From the surveys, we construct indicators on
symptoms, social distancing, vaccination, and other attitudes and behaviors
related to COVID.

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{backfill-compare.pdf}
  \caption{The 95th percentiles of relative error of early reported values of
    key signals compared to final values reported much later. For each date
    between October 15, 2020 and April 15, 2021, the values for each state
    reported between 10 and 90 days later are compared to ``final'' versions
    recorded as of August 13, 2021. Even officially reported case and death data
    can have large revisions 30--60 days or more after initial reporting; much
    of this is driven by individual large revisions affecting specific states
    and dates, rather than systematic changes affecting all states and dates.}
  \label{fig:backfill-compare}
\end{figure}

>>>>

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID-19 Trends and Impact Survey receives an average of 50,000
responses daily, and has received over 25 million responses since April 2020
\cite{Salomon:2021, Kreuter:2020}. From the surveys, we construct indicators on
symptoms, social distancing, vaccination, and other attitudes and behaviors
related to COVID. The surveys are voluntary and participants are redirected to a
platform managed by Carnegie Mellon University to give consent and take the
survey; individual response data is not provided to Facebook and the data
collection protocol was approved by the Carnegie Mellon Institutional Review
Board (STUDY2020\_00000162).

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/backfill-compare.pdf}
  \caption{The 95th percentiles of relative error of early reported values of
    key signals compared to final values reported much later. For each date
    between October 15, 2020 and April 15, 2021, the values for each state
    reported between 10 and 90 days later are compared to ``final'' versions
    recorded as of August 13, 2021. Even officially reported case and death data
    can have large revisions 30--60 days or more after initial reporting; much
    of this is driven by individual large revisions affecting specific states
    and dates, rather than systematic changes affecting all states and dates.}
  \label{fig:backfill-compare}
\end{figure}
